Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-10-06 manuscript/tables&figures.Rmd
Swapped Figs 3-4, added text to legends #150

**Figure 3. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b), across species for the three focal droughts.** Species codes are given in Table 2. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package [@R-agricolae].

**Figure 4. Visualization of best statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** Confidence intervals were defined via bootsrapping in the  bootpredictlme4 package. Model coefficients are given in Tables S8 and S10-11.

@@

![**Figure 3. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b), across species for the three focal droughts.** Species codes are given in Table 2.  See Fig. S7 for parallel plot for recovery ($Rc$).](tables_figures/publication/Figure3_Rt-Rs_across_sp.png)

@@

![**Figure 4. Visualization of top statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** For cases where the best model includes a DBH x TWI interaction ($Rc$ in all droughts and 1966, $Rs$ in all droughts and 1977), we plot the best model without the interaction. Visualization of the best mixed effects model per drought scenario was created by the visreg package [@R-visreg], and confidence intervals were defined via bootsrapping in the bootpredictlme4 package. Model coefficients are given in Tables S8 and S10-11. ](tables_figures/publication/Figure4_model_vis_all.png)

>>>>

**Figure 3. Visualization of top statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** For cases where the best model includes a DBH x TWI interaction ($Rc$ in all droughts and 1966, $Rs$ in all droughts and 1977), we plot the best model without the interaction. Visualization of the best mixed effects model per drought scenario was created by the *visreg* package in R, and confidence intervals were defined via bootsrapping in the *bootpredictlme4* package. Model coefficients are given in Tables S8 and S10-11. Descriptions of variables (e.g. $ln[H]$ can be found in Table 3.

**Figure 4. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b) value ranges across species for the three focal droughts.** Species codes are given in Table 2, and closed dots represent outliers from the main boxplots. The dotted line at y=1 represents no change in $Rt$ or $Rs$ from the previous year. Letters illustrate significance groupings per year (colored and ordered, top to bottom, 1966, 1977, 1999). That is, a group of species with the same letter above their boxplot (e.g. "b") are statistically different from species in another group (e.g. "a"). Letter groupings do not transfer across variables $Rt$ and $Rs$. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package in R. Descriptions of variables (e.g. $ln[H]$ can be found in Table 3.

@@

![**Figure 3. Visualization of top statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** For cases where the best model includes a DBH x TWI interaction ($Rc$ in all droughts and 1966, $Rs$ in all droughts and 1977), we plot the best model without the interaction. Visualization of the best mixed effects model per drought scenario was created by the *visreg* package in R, and confidence intervals were defined via bootsrapping in the *bootpredictlme4* package. Model coefficients are given in Tables S8 and S10-11. Descriptions of variables (e.g. $ln[H]$ can be found in Table 3.)
](tables_figures/publication/Figure3_model_vis_all.png)

@@

![**Figure 4. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b) value ranges across species for the three focal droughts.** Species codes are given in Table 2, and closed dots represent outliers from the main boxplots. The dotted line at y=1 represents no change in $Rt$ or $Rs$ from the previous year. Letters illustrate significance groupings per year (colored and ordered, top to bottom, 1966, 1977, 1999). That is, a group of species with the same letter above their boxplot (e.g. "b") are statistically different from species in another group (e.g. "a"). Letter groupings do not transfer across variables $Rt$ and $Rs$. See Fig. S7 for parallel plot for recovery ($Rc$). Analysis conducted using *agricolae* package in R.](tables_figures/publication/Figure4_Rt-Rs_across_sp.png)
